### 2020-04-15 serial.tex
a small push

\begin{flushleft}{
	\Large
	\textbf\newline{
		Unraveling the paradox between generation and serial intervals
	}
}
\newline\\
Sang Woo Park
\end{flushleft}

@@

Using cohort-based approaches, we can define forward and backward serial intervals.
The forward serial-interval distribution describes the

>>>>

\begin{flushleft}{
	\Large
	\textbf\newline{
		Unraveling the paradox between generation and serial intervals: applications to COVID-19 pandemic
	}
}
\newline\\
Sang Woo Park
\end{flushleft}

@@

Using cohort-based approaches, we define forward and backward serial intervals.
The forward serial-interval distribution describes the renewal process of the
